---
title: "PARTNER"
author: "J. Lucas McKay"
date: "10/29/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, collapse = T, message = F, warning = F)
```

## Partner

etc.

```{r cars}
library(tidyverse)
source("utilities.R")
```

## Workflow

1. Modify report on Redcap.
2. Download data (code below).
3. Create tables of data indicating missing/extreme values.
4. Fix missing/extreme values.
5. Return to 1.

## Baseline demographic and clinical characteristics

Baseline and clinical characteristics at Redcap event `baseline_arm_3` are as follows:

```{r}

d = DownloadData()

 redcap_event_names = c(
 "screening_arm_2",
 "informed_consent_arm_2",
 "prefg_arm_1",
 "randomization_arm_3",
 "baseline_arm_3",
 "3month_arm_3",
 "78_month_screening_arm_3",
 "12month_arm_3",
 "intervention_arm_3",
 "monthly_checkin_arm_3") 

d_baseline_arm_3 = DownloadData("baseline_arm_3")
d_3month_arm_3 = DownloadData("3month_arm_3")
 
arsenal::tableby(~Age+Sex+MoCA+BDIII, data = d_baseline_arm_3) |> summary(digits=1) |> knitr::kable()
```

## Cognitive outcomes

Cognitive outcomes at Redcap event `3month_arm_3` are as follows:

```{r}
arsenal::tableby(~MoCA, data = d_3month_arm_3) |> summary(digits=1) |> knitr::kable()
```


## Screen missing values

```{r}
FindMissing(d_baseline_arm_3,"MoCA")
FindMissing(d_baseline_arm_3,"Age")
FindMissing(d_baseline_arm_3,"Sex")
```

